\Title

### 2016-02-14 manuscript/manuscript.tex
Figure for SAm data stages in processing
Grouped the sediment model in this figure as well. Replaces the old data
figure. Will put the final gravity data in a separate figure.

Placeholders for figures in the paper.
Map of the sediment-free Bouguer for SAm
Figure for the Assumpção seismic data
Remove width setting in figures
Don't need it and it messes up figures when using manuscript mode.
Add width only to full page figures
The page width in manuscript mode is smaller than 7in so I need this.
Figure for the estimated Moho depth for SAm
Plot seismic diff in same figure as inversion results
Fi

%\documentclass[]{article}
%\usepackage{natbib}
% \documentclass[extra,mreferee]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}

@@

% Useful commands
% ===============

@@

% Sketches to explain the methodology

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and
        the corresponding density anomalies after removal of the normal gravity:
        topography, oceans, crustal heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/cv-grid-separation}
    \caption{Sketch of a data grid separated into
        the training (white dots with black outlines)
        and testing (black dots) data sets.
        The training data set is still displayed on a regular grid
        but with twice the grid spacing
        of the original data grid.}
    \label{fig:grid_separation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:simple-data}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[]{figures/synthetic-simple-results}
    \caption{
        Results from the inversion of the simple synthetic data.
        (a) The estimated Moho depth.
        (b) The difference between the true model depths
        and the estimated depths.
        (c) The inversion residuals (observed data minus
        the data predicted by the estimate).
        (d) Normalized histogram of the residuals. Also shown are the calculated
        mean and standard deviation (std) of the residuals.
        Note that the data were contaminated with normally distributed
        pseudo-random noise with zero mean and 5 mGal standard deviation.
        (e) Cross-validation curve used to determine the optimal regularization
        parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.00046$ (red triangle).
        (f) Goal function value (Eq.~\ref{eq:goalfunction}) per Gauss-Newton
        iteration showing the convergence of the gradient descent.
    }
    \label{fig:simple-results}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Synthetic seismic data simulating point estimates of Moho depth.
        The point estimates were obtained by interpolating
        the Moho depth in (a).
    }
    \label{fig:crust1-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[]{figures/synthetic-crust1-results}
    \caption{
    CRUST1 results.
    }
    \label{fig:crust1-results}
\end{figure*}

@@

\subsection{Gravity data}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/sam-gravity-data}
    \caption{This is a figure caption.}
    \label{fig:sam-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/sam-gravity-sed}
    \caption{This is a figure caption.}
    \label{fig:sam-sed}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

>>>>

%\documentclass[]{article}
%\usepackage{natbib}
\documentclass[extra,mreferee]{gji}
% \documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}

@@

@@

\begin{figure}
    \centering
    \includegraphics{figures/problem-concept}
    \caption{
        Sketch of the stages in gravity data correction and
        the discretization of the anomalous Moho relief using tesseroids.
        (a) The Earth and the measured gravity at point P ($g(P)$).
        (b) The Normal Earth and the calculated normal gravity at point P
        ($\gamma(P)$). $z_{ref}$ is the depth of the Normal Earth Moho.
        (c) The gravity disturbance ($\delta(P)$) and
        the corresponding density anomalies after removal of the normal gravity:
        topography, oceans, crustal heterogeneities, and the anomalous Moho.
        (d) The Bouguer disturbance ($\delta_{bg}(P)$) after topographic
        correction and the remaining density anomalies.
        (e) All density anomalies save the anomalous Moho are assumed to have
        been removed before inversion.
        (f) The discretization of the anomalous Moho in tesseroids. Grey
        tesseroids will have a negative density contrast while red tesseroids
        will have a positive one.
    }
    \label{fig:anomalysketch}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/tesseroid-coord-sys}
    \caption{Sketch of a tesseroid (spherical prism) in a geocentric coordinate
        system (X, Y, Z).
        Observations are made at point P with respect to it's local
        North-oriented coordinate system (x, y, z).
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/cv-grid-separation}
    \caption{Sketch of a data grid separated into
        the training (white dots with black outlines)
        and testing (black dots) data sets.
        The training data set is still displayed on a regular grid
        but with twice the grid spacing
        of the original data grid.}
    \label{fig:grid_separation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:simple-data}
\end{figure}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-simple-results}
    \caption{
        Results from the inversion of the simple synthetic data.
        (a) The estimated Moho depth.
        (b) The difference between the true model depths
        and the estimated depths.
        (c) The inversion residuals (observed data minus
        the data predicted by the estimate).
        (d) Histogram of the residuals. Also shown are the calculated
        mean and standard deviation (std) of the residuals.
        Note that the data were contaminated with normally distributed
        pseudo-random noise with zero mean and 5 mGal standard deviation.
        (e) Cross-validation curve used to determine the optimal regularization
        parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.00046$ (red triangle).
        (f) Goal function value (Eq.~\ref{eq:goalfunction}) per Gauss-Newton
        iteration showing the convergence of the gradient descent.
    }
    \label{fig:simple-results}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-data}
    \caption{
        Synthetic data of a model derived from CRUST1.0.
        The model is made of tesseroids with an constant density-contrast
        of $\Delta\rho = 350\ kg/m^3$ and assuming a reference level of
        $z_{ref} = 30\ km$.
        (a) The Moho depth of the model in kilometers.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model.
        (c) Synthetic seismic data simulating point estimates of Moho depth.
        The point estimates were obtained by interpolating
        the Moho depth in (a).
    }
    \label{fig:crust1-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) The estimated Moho depth.
        (b) The inversion residuals (observed minus predicted data).
        (c) Histogram of the residuals shown in (b).
        (d) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (e) difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:crust1-data}a)
        and the estimated depths.
        (f) Difference between the synthetic seismic observations
        (Fig.~\ref{fig:crust1-data}c)
        and the estimated depths.
        (g) Histogram of the differences shown in (f).
        (h) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:msehyper}) in $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
    }
    \label{fig:crust1-results}
\end{figure*}

@@

\subsection{Gravity and seismic data}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-corrections}
    \caption{Gravity data and corrections.}
    \label{fig:sam-corrections}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-data}
    \caption{Input data for the inversion.
        (a) Sediment-free Bouguer disturbance for South America.
        (b) Map of seismic point estimates of Moho depth.}
    \label{fig:sam-data}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-moho}
    \caption{The estimated Moho of South America.}
    \label{fig:sam-moho}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/south-america-residuals}
    \caption{Residuals with histogram and convergence.}
    \label{fig:sam-residuals}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figures/south-america-cv}
    \caption{Cross-validation.}
    \label{fig:sam-cv}
\end{figure}
